13th International Satisfiability Modulo Theories Competition (SMT-COMP 2018): Rules and Procedures

### 2018-07-14 rules/rules18.tex
Minor clarification: named terms are not used
Add link to solver submission form
Update rules (after the fact, for future reference)

\newcommand{\rem}[1]{\textcolor{red}{[#1]}}

@@

The rest of this document, revised from the previous
version,\footnote{Earlier versions of this document include
  contributions from Clark Barrett, Roberto Bruttomesso, David Cok,
  Sylvain Conchon, David D{\'e}harbe, Morgan Deters, Alberto Griggio,
  Matthias Heizmann, Albert Oliveras, Giles Reger, Aaron Stump, and
  Tjark Weber.}  describes the rules and competition procedures for
SMT-COMP~2018.  The principal changes from the previous competition
rules are the following:
\begin{itemize}
\item The organizers plan to recognize additional special
  contributions.  These might include:
  \begin{itemize}
  \item Best application track solver (awarded based on a
    competition-wide scoring for the application track)
  \item Best unsat-core track solver (awarded based on a
    competition-wide scoring for the unsat-core track)
  \item Best complementary solver (awarded to the solver that performs
    best when all benchmarks solved by the winning solver are removed)
  \item Most unique solver (awarded to the solver that performs best
    on benchmarks solved by only one solver)
  \item The Prophet (awarded to the solver that performs best on
    benchmarks with unknown status)
  \item The 10 Second Wonder (awarded to the solver that would have
    won if the time limit was 10 seconds)
  \end{itemize}
  The details are still being discussed and subject to change.

\item The time limit per solver/benchmark pair is anticipated to be at
  most 20 minutes in the main track, and at most 40 minutes in the
  other tracks.  \emph{Rationale:} Already in 2017, the time limit for
  the main track was reduced to 20 minutes (down from 40 minutes in
  earlier years) to cope with the inclusion of a large number of
  benchmarks with unknown status.

@@

\item In 2017, the competition featured experimental divisions for
  benchmarks that use algebraic datatypes.  Provided the competition
  tools can be enhanced in time to support datatypes, these divisions
  may become regular (non-experimental) in 2018. \emph{Rationale:}
  Algebraic datatypes are specified in the latest official release
  (Version~2.6) of the SMT-LIB standard.

\item The competition may feature experimental divisions for
  benchmarks that use strings, and for benchmarks that use
  transcendental functions.  \emph{Rationale:} Corresponding theories
  and benchmarks are expected to be added to SMT-LIB in the near
  future.
\end{itemize}

@@

For participation in SMT-COMP, a solver must be uploaded to StarExec
and made publicly available.  StarExec supports solver configurations;
for clarity, \emph{each submitted solver must have one configuration
  only}.  Moreover, the organizers must be informed of the solver's
presence \emph{and the tracks and divisions in which it is
  participating} via the web form at
\begin{center}
  \rem{{\tt TBA}}
\end{center}
A submission must also include a 32-bit unsigned integer.  These
integer numbers, collected from all submissions, are used to seed the
benchmark scrambler.

@@

The benchmark script is in the concrete syntax of the SMT-LIB format,
version~2.6, though with a restricted set of commands.  A benchmark
script is a text file containing a sequence of SMT-LIB commands that
satisfies the following requirements:
%
\begin{enumerate}
\item
  \begin{enumerate}
  \item In the main and unsat-core track, there may be a single
    \akey{(set-option :print-success ...)} command.  Note that
    \texttt{success} outputs are ignored by the post-processor used by
    the competition.\footnote{SMT-LIB~2.6 requires solvers to produce
      a \texttt{success} answer after each \akey{set-logic},
      \akey{declare-sort}, \akey{declare-fun} and \akey{assert}
      command (among others), unless the option \akey{:print-success}
      is set to false.  Ignoring the \texttt{success} outputs allows
      for submitting fully SMT-LIB~2.6 compliant solvers without the
      need for a wrapper script, while still allowing entrants of
      previous competitions to run without changes.}
  \item In the application track, the \akey{:print-success} option
    must not be disabled.  The trace executor will send an initial
      \akey{(set-option :print-success true)} command to the solver.
  \end{enumerate}
\item In the unsat-core track, there is a single \akey{(set-option
  :produce-unsat-cores true)} command.
\item The (single) \akey{set-logic} command setting the benchmark's
  logic is the first command after any \akey{set-option} commands.
\item The script may contain any number of \akey{set-info} commands.
\item The script may contain any number of \akey{declare-sort} and
  \akey{define-sort} commands.  All sorts declared or defined with
  these commands must have zero arity.
\item The script may contain any number of \akey{declare-fun} and
  \akey{define-fun} commands.
\item If the benchmark's logic features algebraic datatypes, the
  script may contain any number of \akey{declare-datatype(s)}
  commands.
\item The script may contain any number of \akey{assert} commands.
  All formulas in the script belong to the benchmark's logic, with any
  free symbols declared in the script.
\item
  \begin{enumerate}
    \item In the main and application track, named formulas are not
      used.
    \item In the unsat core track, top-level assertions may be named.
  \end{enumerate}
\item
  \begin{enumerate}
  \item In the main and unsat-core track, there is exactly one
    \akey{check-sat} command.
  \item In the application track, there are one or more
    \akey{check-sat} commands.  There may also be zero or more
    \akey{push 1} commands, and zero or more \akey{pop 1} commands,
    consistent with the use of those commands in the SMT-LIB standard.
  \end{enumerate}
\item In the unsat-core track, the \akey{check-sat} command (which is
  always issued in an unsatisfiable context) is followed by a single
  \akey{get-unsat-core} command.
\item The script may optionally contain an \akey{exit} command as its
  last command.  In the application track, this command must not be
  omitted.
\item No other commands besides the ones just mentioned may be used.
\end{enumerate}
%
The SMT-LIB format specification is available from the ``Standard''
section of the SMT-LIB website~\cite{SMT-LIB}.  Solvers will be given
formulas only from the divisions into which they have been entered.

@@

>>>>

@@

The rest of this document, revised from the previous
version,\footnote{Earlier versions of this document include
  contributions from Clark Barrett, Roberto Bruttomesso, David Cok,
  Sylvain Conchon, David D{\'e}harbe, Morgan Deters, Alberto Griggio,
  Matthias Heizmann, Albert Oliveras, Giles Reger, Aaron Stump, and
  Tjark Weber.}  describes the rules and competition procedures for
SMT-COMP~2018.  The principal changes from the previous competition
rules are the following:
\begin{itemize}
\item The time limit per solver/benchmark pair is anticipated to be at
  most 20 minutes in the main track, and at most 40 minutes in the
  other tracks.  \emph{Rationale:} Already in 2017, the time limit for
  the main track was reduced to 20 minutes (down from 40 minutes in
  earlier years) to cope with the inclusion of a large number of
  benchmarks with unknown status.

@@

\item In 2017, the competition featured experimental divisions for
  benchmarks that use algebraic datatypes.  These divisions will be
  regular (non-experimental) in 2018. \emph{Rationale:} Algebraic
  datatypes are specified in the latest official release (Version~2.6)
  of the SMT-LIB standard.

\item The competition will feature an experimental divisions for
  benchmarks that use strings.  \emph{Rationale:} Corresponding
  theories and benchmarks are expected to be added to SMT-LIB in the
  near future.
\end{itemize}

@@

For participation in SMT-COMP, a solver must be uploaded to StarExec
and made publicly available.  StarExec supports solver configurations;
for clarity, \emph{each submitted solver must have one configuration
  only}.  Moreover, the organizers must be informed of the solver's
presence \emph{and the tracks and divisions in which it is
  participating} via the web form at
\begin{center}
  \url{https://goo.gl/forms/3pAMFHsfDJqGqucR2}
\end{center}
A submission must also include a 32-bit unsigned integer.  These
integer numbers, collected from all submissions, are used to seed the
benchmark scrambler.

@@

The benchmark script is in the concrete syntax of the SMT-LIB format,
version~2.6, though with a restricted set of commands.  A benchmark
script is a text file containing a sequence of SMT-LIB commands that
satisfies the following requirements:
%
\begin{enumerate}
\item
  \begin{enumerate}
  \item In the main and unsat-core track, there may be a single
    \akey{(set-option :print-success ...)} command.  Note that
    \texttt{success} outputs are ignored by the post-processor used by
    the competition.\footnote{SMT-LIB~2.6 requires solvers to produce
      a \texttt{success} answer after each \akey{set-logic},
      \akey{declare-sort}, \akey{declare-fun} and \akey{assert}
      command (among others), unless the option \akey{:print-success}
      is set to false.  Ignoring the \texttt{success} outputs allows
      for submitting fully SMT-LIB~2.6 compliant solvers without the
      need for a wrapper script, while still allowing entrants of
      previous competitions to run without changes.}
  \item In the application track, the \akey{:print-success} option
    must not be disabled.  The trace executor will send an initial
      \akey{(set-option :print-success true)} command to the solver.
  \end{enumerate}
\item In the unsat-core track, there is a single \akey{(set-option
  :produce-unsat-cores true)} command.
\item The (single) \akey{set-logic} command setting the benchmark's
  logic is the first command after any \akey{set-option} commands.
\item The script may contain any number of \akey{set-info} commands.
\item The script may contain any number of \akey{declare-sort} and
  \akey{define-sort} commands.  All sorts declared or defined with
  these commands must have zero arity.
\item The script may contain any number of \akey{declare-fun} and
  \akey{define-fun} commands.
\item If the benchmark's logic features algebraic datatypes, the
  script may contain any number of \akey{declare-datatype(s)}
  commands.
\item The script may contain any number of \akey{assert} commands.
  All formulas in the script belong to the benchmark's logic, with any
  free symbols declared in the script.
\item
  \begin{enumerate}
    \item In the main and application track, named terms (i.e., terms
      with the \akey{:named} attribute) are not used.
    \item In the unsat core track, top-level assertions may be named.
  \end{enumerate}
\item
  \begin{enumerate}
  \item In the main and unsat-core track, there is exactly one
    \akey{check-sat} command.
  \item In the application track, there are one or more
    \akey{check-sat} commands.  There may also be zero or more
    \akey{push 1} commands, and zero or more \akey{pop 1} commands,
    consistent with the use of those commands in the SMT-LIB standard.
  \end{enumerate}
\item In the unsat-core track, the \akey{check-sat} command (which is
  always issued in an unsatisfiable context) is followed by a single
  \akey{get-unsat-core} command.
\item The script may optionally contain an \akey{exit} command as its
  last command.  In the application track, this command must not be
  omitted.
\item No other commands besides the ones just mentioned may be used.
\end{enumerate}
%
The SMT-LIB format specification is available from the ``Standard''
section of the SMT-LIB website~\cite{SMT-LIB}.  Solvers will be given
formulas only from the divisions into which they have been entered.

@@

As part of the FLoC Olympic Games, Kurt G{\"o}del medals will be
awarded to:
%
\begin{itemize}
\item The best three solvers according to the competition-wide scoring
  (main track);
\item the solver that wins the most competitive divisions in the
  application track;
\item the solver that wins the most competitive divisions in the
  unsat-core track;
\item the solver that wins the QF\_BV division (separately for
  parallel and sequential performance) in the main track.
\end{itemize}
